Security Audit of Safeplug

### 2014-02-17 report/usability.tex
added graph
added description of latency

\subsection{Latency}
This is a to do item for Annie.

>>>>

\subsection{Latency}
If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.  Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).  We recorded the time for a web request on the following settings:

\begin{itemize}
\item Plain Firefox
\item Firefox, no Tor, no ad-blocking
\item Firefox, Tor, no ad-blocking
\item Firefox, Tor, ad-blocking
\item Firefox, no Tor, ad-blocking
\item Tor Browser Bundle with Safeplug
\item Tor Browser Bundle
\end{itemize}

For each of the settings, we took 20 measurements; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.  The differences between web pages can most likely be attributed to the amount of ads on the web page.

It is interesting to note that the average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least. This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad; \url{www.google.com} does not have any ads.  This does not explain why the average latency was greater than the other settings for \url{www.washingtonpost.com}.

We expected the average latency for the Tor Browser Bundle with the Safeplug to be uniformly greater than the average latency of the Tor Browser Bundle, however that was not the case. [Comment: do we have any reasons why this might have happened?]

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.7\textwidth]{latency2}
\caption{Latency of web requests.}
\label{fig:latency2}
\end{center}
\end{figure}
